Summary Tables

### 2020-01-27 summary_tables_outcomes.Rmd
Instead of hardcoded case study, Accra, use the first index of the cities to get column names

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')

# round to
round_to <- 1

@@

scen_prop <- io$scen_prop
io <- io[-2]
for(i in 1:length(io)) {
  io[[i]]$demographic$age[io[[i]]$demographic$age=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths$age_cat[io[[i]]$outcomes$hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$ylls$age_cat[io[[i]]$outcomes$hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$deaths$age_cat[io[[i]]$outcomes$pathway_hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$ylls$age_cat[io[[i]]$outcomes$pathway_hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths <- io[[i]]$outcomes$hb$deaths[,!sapply(names(io[[i]]$outcomes$hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$hb$ylls <- io[[i]]$outcomes$hb$ylls[,!sapply(names(io[[i]]$outcomes$hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$deaths <- io[[i]]$outcomes$pathway_hb$deaths[,!sapply(names(io[[i]]$outcomes$pathway_hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$ylls <- io[[i]]$outcomes$pathway_hb$ylls[,!sapply(names(io[[i]]$outcomes$pathway_hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
}
for(city in cities)
  for(type in c('hb','pathway_hb'))
    for(out in c('deaths','ylls'))
      io[[city]]$outcomes[[type]][[out]] <- collapse_ages(io[[city]]$outcomes[[type]][[out]])
for(city in cities) io[[city]]$demographic <- collapse_ages(io[[city]]$demographic,age_lab='age')
pop_by_age <- lapply(io,function(x)sapply(unique(x$demographic$age),function(y)sum(subset(x$demographic,age==y)$population)))
pop_by_gender <- lapply(io,function(x)sapply(unique(x$demographic$sex),function(y)sum(subset(x$demographic,sex==y)$population)))
injury_col <- which(colnames(io$accra$outcomes$hb$deaths)=='scen1_deaths_inj')
ap_cols <- which(sapply(colnames(io$accra$outcomes$pathway_hb$deaths),function(x)grepl('ap',as.character(x))))
pa_cols <- which(sapply(colnames(io$accra$outcomes$pathway_hb$deaths),function(x)grepl('pa',as.character(x))))
scen_names <- rownames(scen_prop)

>>>>

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota','cape_town', 'vizag')

round_to <- 1

@@

scen_prop <- io$scen_prop
io <- io[-2]
for(i in 1:length(io)) {
  io[[i]]$demographic$age[io[[i]]$demographic$age=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths$age_cat[io[[i]]$outcomes$hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$ylls$age_cat[io[[i]]$outcomes$hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$deaths$age_cat[io[[i]]$outcomes$pathway_hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$ylls$age_cat[io[[i]]$outcomes$pathway_hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths <- io[[i]]$outcomes$hb$deaths[,!sapply(names(io[[i]]$outcomes$hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$hb$ylls <- io[[i]]$outcomes$hb$ylls[,!sapply(names(io[[i]]$outcomes$hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$deaths <- io[[i]]$outcomes$pathway_hb$deaths[,!sapply(names(io[[i]]$outcomes$pathway_hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$ylls <- io[[i]]$outcomes$pathway_hb$ylls[,!sapply(names(io[[i]]$outcomes$pathway_hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
}
for(city in cities)
  for(type in c('hb','pathway_hb'))
    for(out in c('deaths','ylls'))
      io[[city]]$outcomes[[type]][[out]] <- collapse_ages(io[[city]]$outcomes[[type]][[out]])
for(city in cities) io[[city]]$demographic <- collapse_ages(io[[city]]$demographic,age_lab='age')
pop_by_age <- lapply(io,function(x)sapply(unique(x$demographic$age),function(y)sum(subset(x$demographic,age==y)$population)))
pop_by_gender <- lapply(io,function(x)sapply(unique(x$demographic$sex),function(y)sum(subset(x$demographic,sex==y)$population)))
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths)=='scen1_deaths_inj')
ap_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('ap',as.character(x))))
pa_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('pa',as.character(x))))
scen_names <- rownames(scen_prop)
